### 2016-11-04 introduction.tex
more shit

In this work we propose and evaluate a novel algorithm for pruning whole neurons from a trained neural network without any re-training and examine its performance compared to simpler methods. We then analyze the kinds of errors made by our algorithm and use this to launch an investigation into the fundamental nature of learning representations in neural networks. We find that our results corroborate a seemingly forgotten 27-year old observation by \cite{mozer1989skeletonization} concerning the nature of neural network learning. This observation is best summarized in a quotation from \cite{segee1991fault} on the notion of fault-tolerance in multilayer perception networks:

@@

Essentially, \cite{mozer1989using} observed that the behavior of neural networks during training is not to distribute the learning representation evenly or even equitably across hidden units. What actually happens is that a few, elite neurons learn an approximation of the input-output function, and the remaining units simply learn a complex interdependence function which cancels out their respective influence. Furthermore, assuming enough units exist to learn the function in question, increasing the number of parameters does not increase the richness or robustness of the learned approximation, but rather simply increases the number of noisy parameters to be canceled during training. This is evinced by the fact that in many cases, whole neurons can be removed from a network with minimal to no impact on the output approximation, and even more so in the case of networks with copious extraneous units. In other words, there are few bipartisan units in a trained network. A unit is typically either part of the input-output function approximation, or it is part of an elaborate noise cancellation task force. Assuming this is true, most of the compute-time spent training a neural network is likely occupied by this arguably wasteful procedure of silencing superfluous parameters, and pruning is thus a necessary treatment procedure to ``trim the fat.''

>>>>

In this work we propose and evaluate a novel algorithm for pruning whole neurons from a trained neural network without any re-training and examine its performance compared to two simpler methods. We then analyze the kinds of errors made by our algorithm and use this as a stepping off point to launch an investigation into the fundamental nature of learning representations in neural networks. Our results corroborate an insightful though largely forgotten observation by \cite{mozer1989skeletonization} concerning the nature of neural network learning. This observation is best summarized in a quotation from \cite{segee1991fault} on the notion of fault-tolerance in multilayer perceptron networks:

@@

Essentially, \cite{mozer1989using} observed that the behavior of neural networks during training is not to distribute the learning representation evenly or even equitably across hidden units. What actually happens is that a few, elite neurons learn an approximation of the input-output function, and the remaining units must learn a complex interdependence function which cancels out their respective influence. Furthermore, assuming enough units exist to learn the function in question, increasing the number of parameters does not increase the richness or robustness of the learned approximation, but rather simply increases the number of noisy parameters to be canceled during training. This is evinced by the fact that in many cases, whole neurons can be removed from a network with minimal to no impact on the output approximation, and even more so in the case of networks with copious extraneous units. In other words, there are few bipartisan units in a trained network. A unit is typically either part of the input-output function approximation, or it is part of an elaborate noise cancellation task force. Assuming this is true, most of the compute-time spent training a neural network is likely occupied by this arguably wasteful procedure of silencing superfluous parameters, and pruning is thus a necessary treatment procedure to ``trim the fat.''
